### 2017-11-18 README.Rmd
update README

> Kamvar ZN, Amaradasa BS, Jhala R, McCoy S, Steadman JR, Everhart SE. (2017) Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States. *PeerJ Preprints* 5:e3311v1 <https://doi.org/10.7287/peerj.preprints.3311v1>

@@

> Kamvar, Z. N., Amaradasa, B. S., Jhala, R., McCoy, S., Steadman, J. R., & Everhart, S. E. (2017, November). Data and analysis for population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States. <http://doi.org/10.17605/OSF.IO/EJB5Y>

>>>>

> Kamvar ZN, Amaradasa BS, Jhala R, McCoy S, Steadman JR, Everhart SE. (2017) Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States. *PeerJ Preprints* 5:e3311v2 <https://doi.org/10.7287/peerj.preprints.3311v2>

@@

> Kamvar, Z. N., Amaradasa, B. S., Jhala, R., McCoy, S., Steadman, J. R., & Everhart, S. E. (2017, November). Data and analysis for population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States. <https://doi.org/10.17605/OSF.IO/K8WTM>
